Case study validations of automatic bullet matching

### 2018-10-15 index.Rmd
clarification

Regarding requirement (R2), \autoref{fig:compare} shows that a single cutoff value does not exist that separates same-source scores from different-source scores across all three studies, without introducing additional errors.

@@

### Limitations
All of the studies involve the same firearm. We see some variations in scores across different models of Rugers. Likely, we are going to see even bigger variations with different brands of firearms, where there might be different number of lands of different lengths. We also know  that different firearms mark differently well \cite{???}. Rugers are among the firearms that mark very well, so we would correspondingly expect to see lowered similarity scores for other firearms. The matching algorithm works on matching lands. Barrels with polygonal rifling, such as Glocks, do not introduce well defined lands on bullets, which makes an application of the matching algorithm impossible.

>>>>

Regarding requirement (R2), \autoref{fig:compare} shows that a single cutoff value does not exist that separates same-source scores from different-source scores across all three studies, without introducing errors.

@@

### Limitations
All of the studies involve the same type of firearm. We see some variations in scores across different models of Rugers. Likely, we are going to see even bigger variations with different brands of firearms, where there might be different number of lands of different lengths. We also know  that different firearms mark differently well \cite{???}. Rugers are among the firearms that mark very well, so we would correspondingly expect to see lowered similarity scores for other firearms. The matching algorithm works on matching lands. Barrels with polygonal rifling, such as Glocks, do not introduce well defined lands on bullets, which makes an application of the matching algorithm impossible.
